Higher-Order unification for free!

### 2024-04-16 paper/main.tex
clean proof  lemma 5.15

\begin{lemma}
  Given a \linketa $l$, the unification done by \progressetadedup is between
  terms in \wellb.
  \label{lemma:unif-eta-3}
\end{lemma}

\begin{proof}
  We unify the \rhs{} of two \linketa. Both have the
  shape $\lambda x.t$ and by \cref{lemma:unif-eta-aux}, $\wellb(t)$.
\end{proof}

>>>>

\begin{lemma}
  The unification done by \progressetadedup is between
  terms in \wellb.
  \label{lemma:unif-eta-3}
\end{lemma}

\begin{proof}
  Given two \linketa{}s \linketaM{\Gamma_1}{X}{\lambda x.t} and
  \linketaM{\Gamma_2}{Y}{\lambda x.t'} 
  the unification is performed between $t$ and $t'$. Both terms are
  \wellb and therefore, unification is done between \wellb terms.
\end{proof}
